DOpElib: Differential Equations\\ and Optimization Environment

### 2013-05-09 Examples/PDE/StatPDE/Example7/content.tex
1) Minor changes in the formatting of the documentation. 2) Added documentation to PDE/StatPDE/Example9
Further work on the examples

In this example we consider the stationary incompressible Stokes equation. Here,
we use the symmetric stress tensor which has a little consequence when using 
the do-nothing outflow condition. In strong formulation we have
\begin{align*}
-\nabla\cdot (\nabla v + \nabla v^{T}) + \nabla p &= f \\
\operatorname{div}\, v &= 0 
\end{align*}
on the domain $\Omega = [-6,6]\times [0,2]$. We choose for simplicity $f=0$.

>>>>

\subsubsection{General problem description}
This is the simple vector valued laplace equation on the unitsquare with righthandside $(1,1)$ and zero dirichlet values. The classical example of a PDE.
